Supplementary material

### 2019-04-17 Manuscript/ms.tex
A few discussion tweaks

While mosquito population dynamics play an important part in determining the effectiveness of control interventions, their role is also closely coupled with human immune processes.
In addition to controlling how strongly a mosquito control intervention propagates into the following year, human immune processes also influence the overall vulnerability of the system to control.
ten Bosch \emph{et al.} \cite{TenBosch2016} observed similar behavior in their models of dengue dynamics, and found that longer periods of cross-immunity generated systems in which transmission was more difficult to disrupt with control actions.
Accurate prediction of the effects and efficient deployment of mosquito control is likely to depend on our ability to monitor, predict, and manipulate the dynamics of human immunity.
As such, existing mosquito monitoring efforts need to be paired with more detailed clinical surveillance \cite{Morrison2008} and tighter estimates of the period of cross-immunity \cite{TenBosch2016}.
In the absence of, or as a supplement to, such data, mechanistic models like the one developed here, or so-called TSIR frameworks that reconstruct the dynamics of the susceptible class \cite{Finkenstadt2000, Reich2013}, need to be further developed to better inform and understand mosquito control efforts.

>>>>

The posterior correlation between the effectiveness of control, the period of cross-immunity, and the average mosquito mortality rate emphasizes that the impact of mosquito control is jointly regulated by both mosquito population dynamics and human immune processes.
ten Bosch \emph{et al.} \cite{TenBosch2016} observed similar behavior in their models of dengue dynamics, and found that longer periods of cross-immunity generated systems in which transmission was more difficult to disrupt with control actions.
As a result of these relationships, efficient deployment of mosquito control, and accurate prediction of its effects, is likely to depend on our ability to monitor, predict, and manipulate the dynamics of human immunity.
To meet these needs, existing mosquito monitoring efforts need to be paired with more detailed clinical surveillance \cite{Morrison2008} and tighter estimates of the period of cross-immunity \cite{TenBosch2016}.
In the absence of, or as a supplement to, such data, mechanistic models like the one developed here, or so-called TSIR frameworks that reconstruct the dynamics of the susceptible class \cite{Finkenstadt2000, Reich2013}, need to be further developed to better inform and understand mosquito control efforts.
